\subsection{Expected Component Structure}
\label{Sec:Structure}

\paragraph{Definitions}

A class that builds a placeable object: i.e a FixedComp or
derivative. But not a componsite of objects that have their own
offset/angles, even if they have a commong starting origin.

E.g. if many object could have different placement to each other, then
they are a composite (e.g. a beamline). But an object that has a few
objects within it (for example bolts in a flange) and those included
object don't have a variable modified origin relative to the primary
origin. E.g they don't have a local xStep,yStep etc.


If a class is a placeable object then it should inherrit from
FixedComp directly or via one of the FixedComp derivatives in
attachComp.

It will not inherit from FixedUnit or any of its derivatives.



\paragraph{Object}

The object has to satify a number of abstract virtual methods.

void createAll(Simulation\&,const FixedComp\&,const long int);

This is a public method that builds the object. Typically it will call
in order:

\begin{lstlisting}[language=C++]{Name=MainProg}{floatplacement=H}
  populate(FuncDataBase);
  createUnitVector(FixedComp,const long int);
  createSurfaces();
  createObjects(System);
  createLinks();
\end{lstlisting}

It is strongly discouraged to call any of these sub-methods with
different arguments as normally this breaks the expected inheritance
system. For example, if cutting surfaces are needed e.g. a front/back
cut, then use ExternalCut or FrontBackCut, do not pass an FixedComp
and link point to createSurfaces.


It is also highly likely that for simple FixedComp, FixedRotate, and
FixedOffset objects, createUnitVector can be left out because these
base classes provided methods are acceptable e.g.

FixedComp::createUnitVector sets the Origin and basis set.

FixedOffset::createUnitVector -- applied the pre and post rotations
along with the offset movement set by the variables:

Using preXYAngle,preZAngle,xStep,yStep,zStep,xyAngle,zAngle.

FixedRotate::createUnitVector applies the pre- post rotations along
all three axis


Additional functionality of the reOrientate call is made after
applying the rotations and offset. The function is automatically
applied (if called for) in all of the FixedXXX class.

The reOrientate function moves one axis to a another global axis with
the minimum rotation

Example ess model -- e.g. Vespa/Odin/
